peter_models

### 2024-12-13 peter_models.qmd
updating models

# Fitting OLR with interaction terms

@@

ord_mod_interactions <- polr(Q29 ~ Q271_reordered * S3B +
                               race_recoded +
                  age_recoded +
            educ +  # Educational Attainment
            Q21, # Party affiliation
          data = dataset_clean, Hess=TRUE)

@@

pvals_interact <- pnorm(-abs(summary(ord_mod_interactions)$coef[,"t value"]))*2
ctable_interact <- cbind(summary(ord_mod_interactions)$coef,pvals)

@@

# Generate the plot
odds_ratio_plot(ord_mod)

>>>>

# Fitting OLR with interaction terms 
## This is the model we include in the final report.

@@

dataset_clean$Q271_reordered <- factor(dataset_clean$Q271,
                            levels = c("(5) Not at all important",
                                     "(4) Slightly important",
                                     "(3) Moderately important",
                                     "(2) Very important",
                                     "(1) Extremely important"))
dataset_clean$Q29_reordered <- factor(dataset_clean$Q29,
                            levels = c("(4) Not at all interested in politics",
                                     "(3) Not that interested in politics",
                                     "(2) Somewhat interested",
                                     "(1) Very interested in politics"))

ord_mod_interactions <- polr(Q29_reordered ~ Q271_reordered * S3B +
                               race_recoded +
                  age_recoded +
            educ +  # Educational Attainment
            Q21, # Party affiliation
          data = dataset_clean, Hess=TRUE)

@@

pvals_interact <- pnorm(-abs(summary(ord_mod_interactions)$coef[,"t value"]))*2
ctable_interact <- cbind(summary(ord_mod_interactions)$coef,pvals_interact)

@@

# Generate the plot
odds_ratio_plot(ord_mod_interactions)

# Fitting OLR Model with Interaction Term (Q271 * Q21 Party ID)

library(MASS) # package for model
library(caret) # package for confusion matrix

# dataset_clean$Q271_reordered <- factor(dataset_clean$Q271,
#                             levels = c("(5) Not at all important",
#                                      "(4) Slightly important",
#                                      "(3) Moderately important",
#                                      "(2) Very important",
#                                      "(1) Extremely important"))

ord_mod_interactpoliticalID <- polr(Q29 ~ Q271_reordered * Q21 +
                               race_recoded +
                  age_recoded +
            educ +  # Educational Attainment
            S3B, # Gender
          data = dataset_clean, Hess=TRUE)

summary(ord_mod_interactpoliticalID)

pvals_interactpoliticalID <- pnorm(-abs(summary(ord_mod_interactpoliticalID)$coef[,"t value"]))*2
ctable_interactpoliticalID <- cbind(summary(ord_mod_interactpoliticalID)$coef,pvals_interactpoliticalID)

ctable_interactpoliticalID

(exp_coefs_interact <- exp(cbind(OR=coef(ord_mod_interactpoliticalID),confint(ord_mod_interactpoliticalID))))

head(ord_mod_interactpoliticalID$fitted.values)
head(predict(ord_mod_interactpoliticalID))

confusionMatrix(predict(ord_mod_interactpoliticalID), dataset_clean$Q29, mode="everything")
